---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))




.shiny-flow-layout > div { width: 210px;}
require(ggplot2)

#Access data locally:
if ((substr(getwd(),1,1) == "I") ) {
  setwd("I:/PUBLIC/PEDS/R Programs/eHars_Dash/")
  } else if ((substr(getwd(),1,1) == "C") ){
    setwd("C:/Users/elliott/My Documents/R/eHars_Dash/")
    } else if((substr(getwd(),1,2) =="/t")) { setwd("/srv/shiny-server/eHARS_Dash/")
      } else setwd("/srv/connect/apps/eHARS_Dash/") 

if(file.exists("./data/ehars.Rda")){
  load("./data/ehars.Rda")
  } else {
    source("./code/import.R")
    eharsdata(".data/ehars.Rda")
    # eharsdata(".data/ehars.Rda", 'O:/DATA_OUT/LA00/Person/person.csv')

  }


varlst <- c("none", "race","age_cat", "trans_categ","birth_sex")

# if(!is.null(input$var_1) && !is.null(outVar())) {
# observe({
#    if(input$selectall == 0) return(NULL) 
#   else if (input$selectall%%2 == 0) {
#     updateCheckboxGroupInput(session,"variables2",paste("Choose",input$var_1),choices=outVar())
#     } else  {
#       updateCheckboxGroupInput(session,"variables2",paste("Choose",input$var_1),
#                                choices=outVar(),selected=outVar())
#       }
# 
# if(!is.null(input$selectall2) && !is.null(input$var_2) && !is.null(outVar3())){
#   if(input$selectall2 == 0) return(NULL) 
#   else if (input$selectall2%%2 == 0) {
#     updateCheckboxGroupInput(session,"variables3",paste("Choose",input$var_2),choices=outVar3())
#     } else {
#       updateCheckboxGroupInput(session,"variables3",paste("Choose",input$var_2),
#                                choices=outVar3(),selected=outVar3())
#     }
# 
# })
# }

outVar <- reactive({
  vars <- sort(unique(as.vector(ehars[[input$var_1]][ehars[[input$var_1]] != ''])))
  return(vars)
  })

output$variables = renderUI({
      if(!is.null(outVar())){ inputPanel(
      actionLink("selectall","Select All/None"),
      checkboxGroupInput('variables2', paste("Choose",input$var_1), selected=NULL, outVar()))}})

outVar2 <- reactive({
  vars <- unique(c("none",varlst[!(varlst %in% input$var_1)]))
  return(vars)
  })

output$variables2 = renderUI({
  selectInput("var_2", label = "Secondary Variable:",
              choices = outVar2()) 
  })

outVar3 <- reactive({
  vars <- if(!is.null(input$var_2)) sort(unique(as.vector(ehars[[input$var_2]][ehars[[input$var_2]] != ''])))
  return(vars)
  })

output$variables3 = renderUI({
  if(!is.null(outVar3())){inputPanel(
    actionLink("selectall2","Select All/None"),
    checkboxGroupInput('variables3', paste("Choose",input$var_2), selected=NULL, outVar3()))
    }
  })

data5 <- reactive({
  varlst = c("count", input$var1, input$var_1, input$var_2)
  if(length(input$variables2)==0) varlst[3] = "none"
  if(length(input$variables3)==0) varlst[4] = "none"
  varlst = varlst[!(varlst %in% "none")]

  if(!is.null(input$variables2) && !is.null(input$variables3) && !is.null(input$var_1) && !is.null(input$var_2)
     && length(input$variables2) && length(input$variables3) > 0  && !(input$var_1 == "none") && !(input$var_2 == "none")) {
    data = ehars[which(ehars[[input$var_1]] %in% input$variables2 & ehars[[input$var_2]] %in% input$variables3),]
      data2 <- aggregate(data$count, by=list(data[[input$var1]],data[[input$var_1]],data[[input$var_2]]), FUN=sum)
      data2$colgroup <- paste(data2[['Group.2']],data2[['Group.3']])
  } else {
    if(!is.null(input$variables2) && length(input$variables2) > 0 && !is.null(input$var_1) && !(input$var_1 == "none")) {
      data = ehars[which(ehars[[input$var_1]] %in% input$variables2),]
      data2 <- aggregate(data$count, by=list(data[[input$var1]],data[[input$var_1]]), FUN=sum)
      data2$colgroup <- data2[['Group.2']]
      } else {
        if(!is.null(input$variables3) && length(input$variables3) > 0 && !is.null(input$var_2) && !(input$var_2 == "none")) {
          data = ehars[which(ehars[[input$var_2]] %in% input$variables3),]
          data2 <- aggregate(data$count, by=list(data[[input$var1]],data[[input$var_2]]), FUN=sum)
          data2$colgroup <- data2[['Group.2']]
          } else {
            data = ehars
            data2 <- aggregate(data$count, by=list(data[[input$var1]]), FUN=sum)
            }
      }
    }

names(data2)[1] <- input$var1
if (length(varlst)>2) names(data2)[length(names(data2))-1] <- "count"
else names(data2)[length(names(data2))] <- "count"


  data3 <- subset(data2, data2[1]>=input$year1 & data2[1]<=input$year2)

  data3

})

plot4 <- reactive({
  if(length(names(data5()))>3) qplot(data5()[[input$var1]], count, data = data5(), color = data5()$colgroup, xlab=names(data5())[1])
  else qplot(data5()[[input$var1]], count, data = data5(), xlab=names(data5())[1])
        })


output$downloadData <- downloadHandler(
    filename = function() { 'data.csv' },
    content = function(file) {
      write.csv(data5(), file)
    }
  )


shinyUI(  
  fluidPage(
  tags$head(
    tags$link(rel = "stylesheet", type = "text/css", href = "./www/bootstrap.css")),
    tags$head(tags$style(HTML('

    .shiny-flow-layout > div {
     width: 210px;
      }
    '))),

    headerPanel("HIV Diagnoses, AIDS Diagnoses, HIV/AIDS Deaths in Louisiana - Ficitonal Data"),
          inputPanel(
     selectInput("var1", label = "Choose Variable:",
              choices = c("yr_hiv", "yr_aids", "yr_death")),
            selectInput("year1", label = "Start Year:",
              choices = c(1979:2013)),
            selectInput("year2", label = "End Year:",
              choices = c(1979:2013),selected=2013),
            div(),
            selectInput("var_1", label = "Primary Variable:", choices = varlst),
            uiOutput('variables'),
            uiOutput('variables2'),
            uiOutput('variables3')
          ),    
          tabsetPanel(
             tabPanel('plot',     renderPlot(plot4(), width = 1000)),
             tabPanel('table', renderDataTable({ data5() }, options = list(paging = FALSE, searching=FALSE))),
             tabPanel('download', downloadButton('downloadData', 'Download data'))
)
             )


        )

